Footpath Planning for Example-driven Procedural Road Networks

### 2020-04-21 report/report.tex
Update todo
Reorganize Background

The last decade has seen multiple startups in the area of software that aid urban arcitecture. The software uses procedural models to render a city grid based on real-world locations, or generate new user-specified parameters, and allow for varying degrees of manual editing on grid, road, neighbourhood, city block or individual feature level.
Some of the most prominent examples are CityEngine (made by the startup Procedural, bought by ESRI), Urban Canvas (made by the startup Synthicity, bought by Autodesk) and ArcGIS (***).

@@

Procedural city-generation models combine architectural elemets, such as streets, lots, buildings, building facades.

Urban design practises with conventional two-dimenstional deliverables range from delivering neighbourhood designs, urban zoning and building plans, to writing design codes and building ordinances.

@@

% MONDAY
% TODO: Quote Todor's paper for geodata import services and current state of the field
% TODO: RELATED WORK, mention current sources (Haklay, Fan)
% TODO: ANALYSIS SECTION, figure out what to write

% TODO: Collision correction: Fix collisions by relaxing both feature_1 and feature_2

% TUESDAY
% TODO: Collision correction: Edit edge distance function to factor in width of the other path
% TODO: Collision correction run
% TODO: Figure of street, before correction, after correction
% TODO: Table for collision correction data in report

@@

% WEDNESDAY
% TODO: Proof read entire report
% TODO: Start large data run, way collision

>>>>

Procedural city-generation models combine architectural elemets, such as streets, lots, buildings, building facades.
Urban design practises with conventional two-dimenstional deliverables range from delivering neighbourhood designs, urban zoning and building plans, to writing design codes and building ordinances.
The last decade has seen multiple startups in the area of software that aid urban arcitecture. The software uses procedural models to render a city grid based on real-world locations, or generate new user-specified parameters, and allow for varying degrees of manual editing on grid, road, neighbourhood, city block or individual feature level.
Some of the most prominent examples are CityEngine (made by the startup Procedural, bought by ESRI), Urban Canvas (made by the startup Synthicity, bought by Autodesk, now defunct) and ArcGIS (***).

@@

@@

% TUESDAY
% TODO: RELATED WORK, mention current sources (Haklay, Fan)
% TODO: ANALYSIS SECTION, figure out what to write

% TODO: Collision correction: Fix collisions by relaxing both feature_1 and feature_2
% TODO: Collision correction: Edit edge distance function to factor in width of the other path

% WEDNESDAY
% TODO: Collision correction run
% TODO: Figure of street, before correction, after correction
% TODO: Table for collision correction data in report

@@

% THURSDAY
% TODO: Proof read entire report
% TODO: Start large data run, way collision
